Constant Error Tolerance Computational Fuzzy Extractors

### 2014-01-14 constantRate/ConstCompFuzzExt.tex
Fixing proof about maximal probability outcome

\begin{itemize}
\item Show that conditioned on the adversary's view there is a large set of blocks, $\mathcal{I}$, that have a super logarithmic entropy~(\lemref{lem:blocks unguessable after queries}).
\item Show that conditioned on the values of all other indices, $C$ still has many possible values.  That is, $\Hav(C | C_{\mathcal{I}^c})$ is large~(\clref{cl:many locations ent}).
\item Assume that the adversary has perfect knowledge of $C_{\mathcal{I}^c}$.
\item For all codewords $c, c' \in C| C_{\mathcal{I}^c}$, the codewords $c, c'$ are indistinguishable given the adversary's view~(\lemref{lem:codewords in I close}).
%\item The distribution $ C| C_{\mathcal{I}^c} \wedge View(A)$ is close to $C| C_{\mathcal{I}^c}$.  
%\item For all indices in $\mathcal{I}$, the adversary's guess for $c_i, i\in \mathcal{I}$ is close to the prior distribution $C_i | C_{\mathcal{I}^c}$.  
%\item Without seeing a $1$ on a particular block, it is impossible to the distinguish between $c_i=1$ and $c_i=0$.  
%tell if a $1$ or $0$ On all blocks where the probability of a query having returned a $1$ is negligible, it is impossible to tell if you presented with an obfuscation of $W_i$ or a uniform random variable.
% $c_i, i\not \in \mathcal{I}$ there are many possible values of $c\in C$~(\clref{cl:many locations ent}).
%\item Any two codewords, $c_1, c_2\in C | C_{\mathcal{I}^c}$ are statistically close given the adversary's view.
\item The set of codewords $C| View(A) \wedge C_{\mathcal{I}^c}$ has conditional min-entropy~(and thus $C|View(A)$ has conditional min-entropy)~(\corref{cor:avg min after view}).  
\bnote{I think this is wrong as currently written.  We transition from indistinguishability of all pairs to high entropy for the distribution.  This should be true but I think the argument is wrong.}
\item By the security of obfuscation for every adversary $A$, there exists a simulator $S$ such that $C | A^{P_1,..., P_\ell}$ is computationally indistinguishable from $C | S^{\mathcal{O}}$%~(\lemref{lem:obf has hill ent}).
\bnote{I am having a little trouble formalizing this.  Was hoping for HILL entropy but I don't think that's true.  Will we get relaxed HILL entropy?}
\end{itemize}

@@

\bnote{As stated above I don't think this proof is right?}

@@

Let $c\in C|C_{\mathcal{I}^c}$, then $\expe_{View(A)} \Pr[C=c | C_{\mathcal{I}^c} \wedge View(A)] \leq \Pr[C=c | C_{\mathcal{I}^c}]+\ngl(n)$

@@

Let $c\in C|C_{\mathcal{I}^c}$.  Let $P_c =\Pr[C=c | C_{\mathcal{I}^c}]$.  
%Let $e$ be the exponent of the particular negligible value above~(note $e = \omega(1)$).  For $b\in\{0,1\}$, by \lemref{lem:code bits statistically indist}, we have that in expectation each for each $i$, $\Pr[C_i =1 ] = 1/2$. 

@@

\expe_{view \leftarrow View(A^{\mathcal{O}_{(X_1,..., X_\ell)}})}\Pr[C=c | C_{\mathcal{I}^c} \wedge view ] &\leq \Pr[C=c | C_{\mathcal{I}^c} ]+ \ngl(n) = P_c+\ngl(n)\\

@@

If this was not true~(that is in expectation, the probability of $c$ increased by a polynomial factor, then the statistical distance between $c$ and some other codeword $c'$ would be $1/\poly(n)$ violating \lemref{lem:codewords in I close}.

@@

\bnote{I think the right thing to say here is that the entropy is $\geq \max\{ |C|, O(1)\}$ since the $\ngl$ term probably dominates the above.}Equation~\ref{eq:taylor approx} is derived using the Taylor expansion for $\ln(1+x)$, Equation~\ref{eq:taylor trunc} is derived by noting it is a geometric series and thus all terms $i=3,....$ are contained in the second term $i=2$ which is positive, and Equation~\ref{eq:min ent} is derived using \clref{cl:many locations ent}.

>>>>

\begin{itemize}
\item Show that conditioned on the adversary's view there is a large set of blocks, $\mathcal{I}$, that have a super logarithmic entropy~(\lemref{lem:blocks unguessable after queries}).
\item Show that conditioned on the values of all other indices, $C$ still has many possible values.  That is, $\Hav(C | C_{\mathcal{I}^c})$ is large~(\clref{cl:many locations ent}).
\item Assume that the adversary has perfect knowledge of $C_{\mathcal{I}^c}$.
\item For all codewords $c, c' \in C| C_{\mathcal{I}^c}$, the codewords $c, c'$ are indistinguishable given the adversary's view~(\lemref{lem:codewords in I close}).
%\item The distribution $ C| C_{\mathcal{I}^c} \wedge View(A)$ is close to $C| C_{\mathcal{I}^c}$.  
%\item For all indices in $\mathcal{I}$, the adversary's guess for $c_i, i\in \mathcal{I}$ is close to the prior distribution $C_i | C_{\mathcal{I}^c}$.  
%\item Without seeing a $1$ on a particular block, it is impossible to the distinguish between $c_i=1$ and $c_i=0$.  
%tell if a $1$ or $0$ On all blocks where the probability of a query having returned a $1$ is negligible, it is impossible to tell if you presented with an obfuscation of $W_i$ or a uniform random variable.
% $c_i, i\not \in \mathcal{I}$ there are many possible values of $c\in C$~(\clref{cl:many locations ent}).
%\item Any two codewords, $c_1, c_2\in C | C_{\mathcal{I}^c}$ are statistically close given the adversary's view.
\item The set of codewords $C| View(A) \wedge C_{\mathcal{I}^c}$ has conditional min-entropy~(and thus $C|View(A)$ has conditional min-entropy)~(\corref{cor:avg min after view}).  
\item By the security of obfuscation for every adversary $A$, there exists a simulator $S$ such that $C | A^{P_1,..., P_\ell}$ is computationally indistinguishable from $C | S^{\mathcal{O}}$%~(\lemref{lem:obf has hill ent}).
\bnote{I am having a little trouble formalizing this.  Was hoping for HILL entropy but I don't think that's true.  Will we get relaxed HILL entropy?}
\end{itemize}

@@

@@

For all $c\in C|C_{\mathcal{I}^c}$, 
\expe_{View(A)} \Pr[C=c | C_{\mathcal{I}^c} \wedge View(A)] \leq \Pr[C=c | C_{\mathcal{I}^c}]+\ngl(n).

@@

We begin by noting there must exist some $c\in C|C_{\mathcal{I}^c}$ such that 
\expe_{view\leftarrow View}\Pr[C = c | C_{\mathcal{I}^c}] \le \frac{1}{| C| C_{\mathcal{I}^c}|}.
Otherwise the sum of the probabilities of $c\in C | C_{\mathcal{I}^c}$ will be greater than $1$.  Let $c_{min}$ be one such value.
Let $c^*$ be an arbitrary $c^*$ in the support of $C|C_{\mathcal{I}^c}$.  Suppose that there exists some polynomial $1/\poly(n)$ such that 

@@

\expe_{view \leftarrow View(A^{\mathcal{O}_{(X_1,..., X_\ell)}})}\Pr[C=c^* | C_{\mathcal{I}^c} \wedge view ] &\geq \Pr[C=c^* | C_{\mathcal{I}^c} ]+ \frac{1}{\poly(n)} \\

@@

This means that the difference between the expected probability of $c_{min}$ and $c^*$ is at least $1/\poly(n)$.  Thus, there is an unbounded distinguisher that can tell between the two cases, violating the statistical distance property of   \lemref{lem:codewords in I close}.  This is a contradiction and completes the proof.

@@

\bnote{I think the right thing to say here is that the entropy is $\geq \max\{ |C|, \omega(1)\}$ since the $\ngl$ term probably dominates the above.  If we are more precise with the analysis above we can probably make this $\ngl$ more precise and get better bounds.}Equation~\ref{eq:taylor approx} is derived using the Taylor expansion for $\ln(1+x)$, Equation~\ref{eq:taylor trunc} is derived by noting it is a geometric series and thus all terms $i=3,....$ are contained in the second term $i=2$ which is positive, and Equation~\ref{eq:min ent} is derived using \clref{cl:many locations ent}.
